Simultaneous Elicitation of Scoring Rule and Agents Preferences for Robust Winner Determination

### 2020-01-23 draft.tex

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Two ph.} & {sd} \\%& {2 ph. vc} & {sd} \\
			\midrule
			0 & 20.0 & 0 \\%&  &  \\
			25 & 18.851 & 0.125 \\%&  &  \\
			50 & 17.296 & 0.473 \\%&  &  \\
			75 & 15.774 & 0.609 \\%&  &  \\
			100 & 14.707 & 0.597 \\%&  &  \\
			125 & 12.999 & 0.460 \\%&  &  \\
			150 & 11.975 & 0.473 \\%&  &  \\
			175 & 9.999 & 0.609 \\%&  &  \\
			200 & 11.499 & 0.597 \\%&  &  \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Regret in problems of size $(10, 20)$ after $200$ questions.}
	\label{fig:p}
\end{table}

>>>>

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=2, table-number-alignment = right, table-figures-decimal=0]r}
			\toprule
			{p} & {Two ph.} \\
			\midrule
			0 & 20.000 \\
			25 & 18.851 \\
			50 & 17.296 \\
			75 & 15.774 \\
			100 & 14.707 \\
			125 & 12.999 \\
			150 & 11.975 \\
			175 & 9.999 \\
			200 & 11.499 \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Regret in problems of size $(10, 20)$ after $200$ questions (one repetition only).}
	\label{fig:p}
\end{table}
